pirouette: Determining the error BEAST2 makes in inferring a phylogeny

### 2019-03-08 article.tex
Results for 6 percent in nicer table

\begin{table}
\centering
  \begin{tabular}{| r | c | c | c | c | c | c |}
    \hline
    \textbf{Allele}       & \textbf{i} & \textbf{m} & \textbf{o} & \textbf{I} & \textbf{M} & \textbf{O} \\ 
    \hline
    DRB4*0101             & 3752 & 2397 & 62024 & 1061 & 854  & 11952 \\
    HLA-DPA10103-DPB10402 & 4335 & 2328 & 69040 & 478  & 923  & 4936 \\
    DQA1*0501/DQB1*0301   & 3321 & 1329 & 45461 & 1492 & 1922 & 28515 \\
    \hline 
  \end{tabular}
  \caption{
    Results \richel{These are preliminary, 6 percent of proteome}
  }
  \label{tab:results}
\end{table}

>>>>

\begin{table}
\centering
  \begin{tabular}{| r | c | c | c | c | c | c |}
    \hline
    \textbf{Allele}       & \textbf{i} & \textbf{m} & \textbf{o} & \textbf{I} & \textbf{M} & \textbf{O} \\ 
    \hline
    DRB4*0101             & 3752 & 2397 & 62024 & 1061 & 854  & 11952 \\
    HLA-DPA10103-DPB10402 & 4335 & 2328 & 69040 & 478  & 923  & 4936 \\
    DQA1*0501/DQB1*0301   & 3321 & 1329 & 45461 & 1492 & 1922 & 28515 \\
    \hline 
  \end{tabular}
  \caption{
    \richel{These are preliminary, 6 percent of proteome}
    Location and binding of amino acids for the alleles.
    i: non-binding and inside, 
    m: non-binding and transmembrane, 
    o: non-binding and outside, 
    I: binding and inside, 
    M: binding and transmembrane, 
    O: binding and outside
  }
  \label{tab:results}
\end{table}
